---
from: markdown+emoji
---

## Definition

The bivariate Gumbel copula with parameter $\theta \ge 1$ is defined by, for all $(u,v)\in ]0,1]^2$,
$$
C_{\theta}\left( u, v \right) = \exp\left( - \left( \left( -\ln(u) \right)^{\theta} + \left( -\ln(v)\right)^{\theta} \right)^{\frac{1}{\theta}} \right)
$$

## Kendall's tau

The Kendall's tau of the bivariate Gumbel copula with parameter $\theta \ge 1$ is equal to
$$
1 - \frac{1}{\theta}
$$

## Coefficient of upper tail dependency

The coefficient of upper tail dependency of the bivariate Gumbel copula with parameter $\theta \ge 1$ is equal to
$$
2 - 2^{\frac{1}{\theta}}
$$

## Coefficient of lower tail dependency

The coefficient of lower tail dependency of the bivariate Gumbel copula with parameter $\theta \ge 1$ is equal to $0$.

## Simulation with R

The following script creates simulations of the bivariate Gumbel copula with `R` using the `copula` package, and prints the first 10 simulations.

```{r}
#| warning: false

# Install the copula package if you haven't already
# install.packages("copula")
# Load the copula package
library(copula)

# Define the parameter for the Gumbel copula (e.g., theta = 6)
theta <- 6

# Create a Gumbel copula object
gumbel_copula <- gumbelCopula(theta, dim = 2)

# Generate random samples from the Gumbel copula
n_samples <- 1000  # Number of samples
set.seed(1) # Set the seed to ensure that the results are reproducible
samples <- rCopula(n_samples, gumbel_copula)

# Print the first few samples
head(samples, n = 10)
```
The following script plots the simulations with `R` using the `plotly` package, which creates interactive graphs.

```{r}
#| warning: false

# Install the plotly package if you haven't already
# install.packages("plotly")
# Load the plotly package
library("plotly")

# Convert the samples matrix to a data frame for plotly
df <- as.data.frame(samples)

# Rename the columns for clarity (optional)
colnames(df) <- c("X", "Y")

# Create a dynamic scatter plot with plotly
plot_ly(df, x = ~X, y = ~Y, type = 'scatter') %>%
layout(title = list(text = "Bivariate Gumbel copula samples - theta = 6"),
  xaxis = list(title = "X-axis (Column 1)"),
  yaxis = list(title = "Y-axis (Column 2)")
)
```

